Modeling vertical-axis cross-flow turbine wakes

### 2015-08-11 paper.tex
Add momentum recovery subsubsection

>>>>

\subsubsection{Momentum recovery}

To get an overall idea of the wake recovery predicted by each model, we
rearrange the streamwise component of the Navier--Stokes equation to isolate
$\partial U / \partial x$---following Bachant and
Wosnik\cite{Bachant2015-JoT}---and compute each term at $X/D = 1$ to compare
with the experimental results.

\begin{figure}[ht]
    \includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
    \caption{Weighted sum normalized momentum recovery terms for each CFD case
        and experiments\cite{Bachant2015-JoT} at $x/D=1$.} \label{fig:recovery}
\end{figure}
